Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-05 paper_jasa.tex
update comments

\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}
Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$. For the regression slope parameter $\beta$ suppose the associated test statistic in classical test be $t_{obs}$ with $p$-value $p_B$. By definition we have

@@

\red{HH: $p_D$ isn't defined yet}

>>>>

\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
\red{MM: This $t$ comes from the idea that a classical $T-test$ is available for which we are describing the visual test. Generalizing it is a little bit technical since for all visual test, we may not have a classical $T-test$. Thus the concept of $F(.)$ is little confusing too. I don't know how deal with this situation here.}\\
Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$. For the regression slope parameter $\beta$ suppose the associated test statistic in classical test be $t_{obs}$ with $p$-value $p_B$. By definition we have

@@

\red{HH: $p_D$ isn't defined yet} \\
\red{MM: $p_D$ and $p_B$ are same, right?}
